PSE Quant Sampling Algorithm

### 2021-03-04 quant_estimate/pse_quant_algo.tex
WIP : Estimation Counts

	// PSE variables
	make_pse_symbolic<int>(&d, sizeof(d), "d_prob_sym", 0, 500);
	// PSE variable : Random Sampling
	std::default_random_engine generator;
	std::uniform_int_distribution<int> distribution(0, 500);

	if (a + b > c + d)
	{
		if (a > b) {
			a = 100;
			b = 500;
		} else {
			a = 500;
			b = 100;
		}
	} else {
		if (c > d) {
			a = 100;
			c = 100;
			b = 600;
			d = distribution(generator);
		} else {
			a = 600;
			c = 600;
			b = 100;
			d = distribution(generator);
		}
	}
	if (a + c > b + d)
	{
		a = 200;
		b = -150;
		c = -20;
		d = distribution(generator);
	}
\end{minted}

>>>>

	// PSE variables
	make_pse_symbolic<int>(&d, sizeof(d), "d_prob_sym", 0, 500);

	// PSE variable : Random Sampling
	std::default_random_engine generator;
	std::uniform_int_distribution<int> distribution(0, 500);

	if (a + b > c + d)
	{
		if (a > b) {
			a = 100;
			b = 500;
		} else {
			a = 500;
			b = 100;
		}
	} else {
		if (c > d) {
			a = 100;
			c = 100;
			b = 600;
			d = distribution(generator);
		} else {
			a = 600;
			c = 600;
			b = 100;
			d = distribution(generator);
		}
	}

	if (a + c > b + d)
	{
		d = distribution(generator);
	}
\end{minted}
